Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-04-05 snTomas.tex
Small edit test

Another nearby bright galaxy to the East of the SN has a spectroscopic
redshift of $z=1.742$.  This redshift was determined from a spectrum
taken with the G141 grism of the HST WFC3-IR camera, collected as part
of the Grism Lens Amplified Survey from Space (GLASS, PI:Treu,
PID:13459, \citealt{Treu:2015}). \change{As we will see in Sections~\ref{sec:Spectroscopy}
and \ref{sec:PhotometricClassification}, the SN data are inconsistent
with that redshift, meaning that this nearby galaxy is a background
object and therefore has no impact on the SN magnification.}

@@

For Type Ia SNe, the SALT2 model has two additional parameters that
control the shape ($x_1$) and color ($c$) of the light curve.  We use
conservative priors here, defined to encompass a range of Type Ia SN
shapes and colors that is broader than typically allowed in
cosmological analyses \citep[see
e.g.,][]{Kessler:2009b,Sullivan:2011,Rest:2014}. For $x_1$ the prior is
a bifurcated Gaussian distribution with mean $\bar{x}_1=0$, dispersion
$\sigma_{x_1}^+={0.9}$ and $\sigma_{x_1}^-={-1.5}$.  The prior for the
color parameter $c$ has $\bar{c}=0.0$, $\sigma_c^-=0.08$, and
$\sigma_c^+=0.54$.  The $c$ parameter in SALT2 combines intrinsic SN
color and extinction due to dust, so the large red tail of this
distribution allows for the possibility of several magnitudes
of dust extinction along the \tomas\ line of sight.

>>>>

Another nearby bright galaxy to the East of the SN has a spectroscopic
redshift of $z=1.742$.  This redshift was determined from a spectrum
taken with the G141 grism of the HST WFC3-IR camera, collected as part
of the Grism Lens Amplified Survey from Space (GLASS, PI:Treu,
PID:13459, \citealt{Treu:2015}). \change{As we will see in Sections~\ref{sec:Spectroscopy}
and \ref{sec:PhotometricClassification}, the SN data are inconsistent
with that redshift, meaning that this spatially nearby galaxy is a background
object and therefore has no impact on the SN magnification.}

@@

For Type Ia SNe, the SALT2 model has two additional parameters that
control the shape ($x_1$) and color ($c$) of the light curve.  We use
conservative priors here, defined to encompass a range of Type Ia SN
shapes and colors that is broader than typically allowed in
cosmological analyses \citep[see
e.g.,][]{Kessler:2009b,Sullivan:2011,Rest:2014}. For $x_1$ the prior is
a bifurcated Gaussian distribution with mean $\bar{x}_1=0$, dispersion
$\sigma_{x_1}^+={0.9}$ and $\sigma_{x_1}^-={-1.5}$.  The prior for the
color parameter $c$ has $\bar{c}=0.0$, $\sigma_c^-=0.08$, and
$\sigma_c^+=0.54$ using the same distribution as for $x_1$.  The $c$ parameter in SALT2 combines intrinsic SN
color and extinction due to dust, so the large red tail of this
distribution allows for the possibility of several magnitudes
of dust extinction along the \tomas\ line of sight.
